### 2017-03-07 index.tex
Sync

                    \begin{itemize}
  \item a\empty info@csarven.ca\item b\empty amy@rhiaro.co.uk\item c\empty langec@cs.uni-bonn.de\item d\empty auer@cs.uni-bonn.de\item e\empty timbl@w3.org
    \end{itemize}

                \begin{description}
  \item[Identifier] \empty http://csarven.ca/linked-data-notifications
    \end{description}

>>>>

                    \begin{itemize}
  \item ✊\empty info@csarven.ca\item 🐦\empty amy@rhiaro.co.uk\item ∫\empty langec@cs.uni-bonn.de\item ⚛\empty auer@cs.uni-bonn.de\item 🕸\empty timbl@w3.org
    \end{itemize}
